---
title: "Transfer -- Developmental Data"
output: html_document
date: "2025-06-03"
---

```{r warning = FALSE, include = FALSE, max.height = '100px'}
#Load libraries.

library(ggpubr)
require(readxl)
library(performance)
require(DT)
require(dplyr)
require(ggplot2)
require(ggsci)
require(lme4)
require(lmerTest)
require(multcomp)
require(emmeans)
library(tidyverse)
library(BayesFactor)
library(bayestestR)
library(broom)
library(patchwork)
library(ggridges)
library(psych)
library(brms)
library(reshape2)
select <- dplyr::select


```


# Load data 
```{r}

no_outliers_data_smarte = read_csv("clean_trial_data_smarte_full.csv") %>% 
    mutate(Grade = factor(Grade, levels=c("K","1","2","3","4","5","7","A"))) 

no_outliers_data = read_csv("clean_trial_data_full.csv") %>% 
    mutate(Grade = factor(Grade, levels=c("K","1","2","3","4","5","7","A"))) 

```

# Figures and Analyses

## Figure 2 RT and Accuracy Plots

```{r}


# Aggregate scores.
DATASET <- do.call(data.frame, aggregate(Array_Submit_RT ~ Participant + Grade, data = no_outliers_data, FUN = function(x) c(Mean = mean(x), L95 = mean(x) - 1.96 * sd(x) / sqrt(length(x)), U95 = mean(x) + 1.96 * sd(x) / sqrt(length(x))), subset = Array_Correct == 1)) %>% 
  filter(Array_Submit_RT.Mean<20)
# Create the plot.
dot_PLOT <- ggplot(data = DATASET, aes(y = Array_Submit_RT.Mean, x = Grade, color = Grade, fill = Grade)) +
geom_point(size = 0.50, position = position_jitter(width = .15), alpha = 0.50) +
geom_boxplot(width = 0.10, outlier.shape = NA, alpha = 0.25) +
  scale_color_d3() +
  scale_fill_d3() +
labs(x = 'Grade', y = '(Correct) Response times') +
scale_x_discrete() + 
# scale_y_continuous(breaks = c(0.00,1000,2000,3000,4000,5000,6000,7000)) + 
# coord_cartesian(ylim = c(0.00, 8000)) +
  ylim(0, 10)+
theme(text = element_text(size = 24)) +
theme_classic() +
# ggtitle("Mean (correct) RT on Non-Symbolic Problems") +
theme(legend.position = "bottom")+
guides(fill = guide_legend(nrow = 1),
       color = guide_legend(nrow = 1))

# Aggregate scores.
DATASET <- do.call(data.frame, aggregate(Symb_Submit_RT ~ Participant + Grade, data = no_outliers_data, FUN = function(x) c(Mean = mean(x), L95 = mean(x) - 1.96 * sd(x) / sqrt(length(x)), U95 = mean(x) + 1.96 * sd(x) / sqrt(length(x))), subset = Array_Correct == 1)) %>% 
  filter(Symb_Submit_RT.Mean<20)
# Create the plot.
digit_PLOT <- ggplot(data = DATASET, aes(y = Symb_Submit_RT.Mean, x = Grade, color = Grade, fill = Grade)) +
geom_point(size = 0.50, position = position_jitter(width = .15), alpha = 0.50) +
geom_boxplot(width = 0.10, outlier.shape = NA, alpha = 0.25) +
  scale_color_d3() +
  scale_fill_d3() +
labs(x = 'Grade', y = '(Correct) Response times') +
scale_x_discrete() + 
# scale_y_continuous(breaks = c(0.00,1000,2000,3000,4000,5000,6000,7000)) + 
# coord_cartesian(ylim = c(0.00, 8000)) +
theme(text = element_text(size = 24)) +
ylim(0, 10)+
theme_classic() +
# ggtitle("Mean (correct) RT on Symbolic Problems") +
theme(legend.position = "bottom")+
guides(fill = guide_legend(nrow = 1),
       color = guide_legend(nrow = 1))


(dot_PLOT | digit_PLOT)+ 
  plot_annotation(tag_levels='A')+
  plot_layout(guides = "collect") & theme(legend.position='bottom',
                                                          legend.key.size = unit(0.6, 'cm'),
                                                          legend.text = element_text(size=13),
                                                          # legend.title = element_text(size=13),
                                          text = element_text(size = 13),
                                          plot.tag = element_text(size = 25))





```

# Developmental Results

```{r}

kids_df = no_outliers_data %>% 
  filter(Group!='Adults') %>% 
  filter(!is.na(Grade)) %>% 
  mutate(Congruence = if_else(Match=='Match',
                              'Numerical Congruence', 'Numerical Incongruence'))

# generate age bins based on median split
age_group_df = kids_df %>% select(Participant, age,Grade)%>% unique() %>% 
  filter(!is.na(age)) %>% 
     mutate(age_group = ntile(age, 2)) %>% 
     mutate(age_group = if_else(age_group==1, 'Younger','Older')) %>% 
  select(Participant,age_group)

kids_df = kids_df %>% inner_join(age_group_df, by='Participant')

# Get information about age group splits

kids_df %>% 
  select(Participant,Grade,age_group) %>% 
  unique() %>% 
  group_by(age_group,Grade) %>% 
  summarise(count=n())

kids_df %>% 
  select(Participant,Grade,age_group,age) %>% 
  unique() %>% 
  group_by(age_group) %>% 
  summarise(count=n(),
            mean_age = mean(age, na.rm=T))
  
```





## Descriptive Statistics

### Accuracy
```{r}
# Accuracy Stats
kids_df %>% 
  group_by(Participant,Grade) %>% 
  summarise(acc_dots = sum(Array_Correct)/n(),
            acc_sym = sum(Symb_Correct)/n()) %>% 
  ungroup() %>% 
  group_by(Grade) %>% 
  summarise(mean_acc_dot = mean(acc_dots, na.rm=T),
            sd_acc_dot = sd(acc_dots, na.rm=T),
            mean_acc_sym = mean(acc_sym, na.rm=T),
            sd_acc_sym = sd(acc_sym, na.rm=T))

acc_stats_df = kids_df %>% 
  group_by(Participant,Grade) %>% 
  summarise(acc_dots = sum(Array_Correct, na.rm=T)/n(),
            acc_sym = sum(Symb_Correct,na.rm=T)/n()) %>% 
  ungroup() %>% 
  pivot_longer(cols = c('acc_dots','acc_sym'),
               names_to = 'response_type',
               values_to = 'acc') %>% 
  mutate(response_type = as.factor(response_type),
         Grade = as.factor(Grade))

anova(lmer(acc~Grade*response_type + (1|Participant), data = acc_stats_df))
anovaBF(acc~Grade*response_type, data = acc_stats_df, whichRandom = 'Participant',whichModels = 'top')

emmeans(lmer(acc~Grade*response_type + (1|Participant), data = acc_stats_df), 
        list(pairwise ~ Grade*response_type),
        adjust = "fdr",
        pbkrtest.limit = 3486)

```

### RT

```{r}
# RT Stats
kids_df %>% 
  filter(Symb_Correct==T) %>% 
  filter(Array_Correct==T) %>% 
  group_by(Grade) %>% 
  summarise(mean_rt_dot = mean(Array_First_RT, na.rm=T),
            sd_rt_dot = sd(Array_First_RT, na.rm=T),
            mean_rt_sym = mean(Symb_First_RT, na.rm=T),
            sd_rt_sym = sd(Symb_First_RT, na.rm=T))

stats_df = kids_df %>% 
  filter(Symb_Correct==T) %>% 
  filter(Array_Correct==T)%>% 
  select(Grade,Array_First_RT, Symb_First_RT, Participant) %>% 
  pivot_longer(cols = c('Array_First_RT','Symb_First_RT'),
               names_to = 'response_type',
               values_to = 'RT') %>% 
  mutate(response_type = as.factor(response_type),
         Grade = as.factor(Grade))

anova(lmer(RT~Grade*response_type + (1|Participant), data = stats_df))
anovaBF(RT~Grade+response_type, data = stats_df, whichRandom = 'Participant',whichModels = 'top')
# t.test(stats_df$Array_First_RT, stats_df$Symb_First_RT)
# ttestBF(stats_df$Array_First_RT, stats_df$Symb_First_RT)

```

# Do Children Show Cardinal Priming Effects?

## How does numerical/structural congruence influence cardinal priming effects?

Are there impacts of grouping strucure on cardinal priming, relative to baseline (random no match)

### Statistical Tests

```{r warning = FALSE, echo = FALSE, }
set.seed(202111208)

stats_df_match = kids_df %>% 
  filter(Symb_Correct==1) %>% 
  mutate(Condition_spec = as.factor(Condition_spec),
         Participant = as.factor(Participant),
         age_group = as.factor(age_group)) %>% 
  mutate(Condition_spec = relevel(Condition_spec, ref = 4)) 


# Fit the full model without interaction.
anova(lmer(Symb_First_RT ~ Condition_spec*age_group + (1|Participant), data = stats_df_match))
BF = anovaBF(Symb_First_RT ~  Condition_spec*age_group,whichRandom = 'Participant',
             data = stats_df_match, whichModels = "top")

1/BF

fit0 = lmer(Symb_First_RT ~ Condition_spec*age_group + (1|Participant), data = stats_df_match)
fit1 = lmer(Symb_First_RT ~ Condition_spec+age_group + (1|Participant), data = stats_df_match)
fit2 = lmer(Symb_First_RT ~ Condition_spec:age_group+age_group + (1|Participant), data = stats_df_match)
fit3 = lmer(Symb_First_RT ~ Condition_spec:age_group+Condition_spec + (1|Participant), data = stats_df_match)

bayesfactor_models(fit1, fit2, fit3, denominator = fit0)

anovaBF(Symb_First_RT~age_group+Condition_spec, data = stats_df_match, whichRandom = 'Participant',whichModels = 'top')


```

## Age Effect Plots


### Figure 3A


```{r}

DATASET <- do.call(data.frame, aggregate(Symb_First_RT ~ age_group + Condition_spec ,
                                         data = kids_df %>% 
                                           mutate(age_group = ntile(age, 2)) %>% 
                                           mutate(age_group = if_else(age_group==1, 'Younger','Older')) %>% 
                                           filter(Symb_Correct==1),  
                                           # filter(Condition!='NoMatch') %>% 
                                           # filter(Match=='Match') ,
                                           FUN = function(x) c(Mean = mean(x), 
                                                               L95 = mean(x) - 1.96 * sd(x) / sqrt(length(x)),
                                                               U95 = mean(x) + 1.96 * sd(x) / sqrt(length(x)))))

Age_effect_PLOT_Bar = DATASET %>% 
  mutate(Condition = case_when(Condition_spec=='NoMatch'~ 'Not Matching',
                               Condition_spec=='Random_SumMatch'~ 'Ungrouped Whole Set Matching',
                               Condition_spec=='Group_SumMatch'~ 'Grouped Whole Set Matching',
                               Condition_spec=='Group_PerfectMatch'~ 'Grouped Subgroup Matching')) %>% 
  mutate(Condition = factor(Condition,levels=c('Not Matching',
                                               'Ungrouped Whole Set Matching',
                                               'Grouped Whole Set Matching',
                                               'Grouped Subgroup Matching'))) %>% 
                                           mutate(age_group = factor(age_group, levels=c("Younger","Older")))%>%
  
ggplot( aes(y = Symb_First_RT.Mean, group=interaction(age_group,Condition),
            x = age_group,color = Condition, fill = Condition)) +
geom_col(position='dodge', aes(color = Condition, fill = Condition),alpha=0.8)+
geom_errorbar(aes(x=age_group,ymin = Symb_First_RT.L95, ymax = Symb_First_RT.U95),
              position=position_dodge(.9), width=0.2,color='black')+
scale_color_npg() +
scale_fill_npg() +
labs(x = 'Grade', y = '(Correct) Response times (ms)') +
# scale_y_continuous(breaks = c( 1.00,1.25,1.50,1.75,2.00,2.25,2.50)) +
# coord_cartesian(ylim = c(0, 2500)) +
theme_classic()+
  theme(legend.key.size = unit(1, 'cm'), #change legend key size
        legend.title = element_text(size=14), #change legend title font size
        legend.text = element_text(size=14),
        legend.position='bottom',
        axis.text=element_text(size=15),
        axis.title=element_text(size=17))+
  guides(fill = guide_legend(nrow = 2),
         color = guide_legend(nrow = 2))

Age_effect_PLOT_Bar 

```



### Pairwise Comparisons of Grouping Manipulations

```{r warning = FALSE, echo = FALSE, }

emmeans(lmer(Symb_First_RT ~ Condition_spec*age_group+(1|Participant), data = stats_df_match), 
        list(pairwise ~ Condition_spec),
        adjust = "fdr",
        pbkrtest.limit = 8258)

conditions = unique((stats_df_match %>%
                      mutate(Condition_spec = as.character(Condition_spec)))$Condition_spec)

for(i in 1:length(conditions)){
  for(j in i:length(conditions)){
    Sys.sleep(0.1)
    
    if(i!=j){
        print(paste(conditions[i], conditions[j]))
        print(ttestBF(x=subset(stats_df_match, Condition_spec == conditions[i])$Symb_First_RT,
                      y=subset(stats_df_match, Condition_spec == conditions[j])$Symb_First_RT))
    }
  }
}


```

### Grade Comparisons
```{r warning = FALSE, echo = FALSE, }

emmeans(lmer(Symb_First_RT ~ Condition_spec*age_group + (1|Participant), data = stats_df_match), 
        list(pairwise ~ age_group),
        adjust = "fdr",
        pbkrtest.limit = 3486)

grades = unique((stats_df_match %>%
                      mutate(Grade = as.character(Grade)))$Grade)

 print(ttestBF(x=subset(stats_df_match, age_group == "Older")$Symb_First_RT,
                        y=subset(stats_df_match, age_group == "Younger")$Symb_First_RT))

# for(i in 1:length(grades)){
#   for(j in i:length(grades)){
#     Sys.sleep(0.1)
#     
#     if(i!=j){
#         print(paste(grades[i], grades[j]))
#         print(ttestBF(x=subset(stats_df_match, Grade == grades[i])$Symb_First_RT,
#                       y=subset(stats_df_match, Grade == grades[j])$Symb_First_RT))
#     }
#   }
# }


```



```{r}

# Helper visualization to understand age*condition interaction

test = emmeans(lmer(Symb_First_RT ~ Condition_spec*age_group+(1|Participant), data = stats_df_match), 
        list(pairwise ~ Condition_spec:age_group),
        adjust = "bonf",
        pbkrtest.limit = 7121)

conditions = unique((stats_df_match %>%
                      mutate(Condition_spec = as.character(Condition_spec)))$Condition_spec)


data.frame(test$`pairwise differences of Condition_spec, age_group`) %>% 
  separate(X1, into=c("pred1","pred2"), sep= ' -' ) %>% 
  filter(substr(pred1,nchar(pred1), nchar(pred1))==substr(pred2,nchar(pred2),nchar(pred2))) %>% 
  select(pred1,pred2,estimate, SE, p.value) %>% 
  mutate(sig = if_else(p.value < 0.05, T, F)) %>% 
  unite('pair', c("pred1","pred2")) %>% 
  mutate(Grade = as.factor(substr(pair, nchar(pair),nchar(pair)))) %>% 
  ggplot(aes(x=pair, y = estimate, alpha=sig))+
  geom_col()+
  geom_errorbar(aes(ymin=estimate-SE, ymax=estimate+SE))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  facet_grid(Grade~.)
  
# Younger: Perfect different from rest. No difference between the other three
# Older: Matching arrays differ from no match arrays


test


```

```{r}

grades=c("Older","Younger")

for(g in 1:length(grades)){
  for(i in 1:length(conditions)){
    for(j in i:length(conditions)){
      Sys.sleep(0.1)
  
      if(i!=j){
        print(grades[g])
          print(paste(conditions[i], conditions[j]))
          print(ttestBF(x=subset(stats_df_match, Condition_spec == conditions[i]& age_group == grades[g])$Symb_First_RT,
                        y=subset(stats_df_match, Condition_spec == conditions[j]& age_group == grades[g])$Symb_First_RT))
      }
    }
  }
}


```




# How does SMARTE relate to priming effects in kids?

```{r}

# Set up data for estimating individual priming effects
ind_data = kids_df %>% 
  filter(Symb_Correct==1) %>% 
  select(Participant, Match, Condition_spec, Symb_First_RT,Grade, age) %>% 
  mutate(NoMatch_dummy = case_when(Condition_spec == 'NoMatch'~ 1,
                                          Condition_spec == 'NoMatch'~ 1,
                                          T~0),
         Match_dummy = case_when(Condition_spec == 'Group_SumMatch'~ 1,
                                          Condition_spec == 'Random_SumMatch'~ 1,
                                          T~0),
         Group_SumMatch_dummy = if_else(Condition_spec == 'Group_SumMatch', 1, 0),
         Random_SumMatch_dummy = if_else(Condition_spec == 'Random_SumMatch',1,0),
         Group_PerfectMatch_dummy = if_else(Condition_spec == 'Group_PerfectMatch', 1, 0),
         Condition_spec = relevel(as.factor(Condition_spec),ref=4),
         Match = relevel(as.factor(Match),ref=2),
         Symb_First_RT = log(Symb_First_RT))%>% 
  mutate(Condition_spec = case_when(Condition_spec == 'Random_NoMatch'~ 'NoMatch',
                                    Condition_spec == 'Group_NoMatch'~ 'NoMatch',
                                    Condition_spec == 'Group_SumMatch' ~ 'Match',
                                    Condition_spec == 'Random_SumMatch' ~ 'Match',
                                    T~Condition_spec),
         grade_num = if_else(Grade=='K',0,as.numeric(Grade))) 



mod0 = lmer(Symb_First_RT ~Match  +(1+Match|Participant),
            data = ind_data,REML=F,
            control = lmerControl(
                           optimizer ='Nelder_Mead'))

summary(mod0)

# Merge data with smarte and estimates of priming effects
kids_df_smarte = kids_df %>% 
  inner_join(ranef(mod0)$Participant %>% 
                    as.data.frame() %>% 
                    rownames_to_column("Participant") %>% 
                    mutate(
                           priming_effectMatch =  -1*(-0.10207+(MatchMatch))),
             by = 'Participant') %>% 
  inner_join(symbolic_smarte_scores, by=c('Participant')) %>% 
  inner_join(group_rcs_df, by=c("Participant")) %>% 
  inner_join(symbolic_module_scores, by=c("Participant"))


```

### Test-retest reliability of priming effects
```{r}


ind_data_session_1 = kids_df %>% 
  group_by(Participant) %>% 
  mutate(trial_num = row_number(),
         Session = if_else(Session=='1','001',Session)) %>% 
  ungroup() %>% 
  filter(Session=='001') %>% 
  filter(Symb_Correct==1) %>% 
  select(Participant, Match, Condition_spec, Symb_First_RT,Grade, age) %>% 
  mutate(NoMatch_dummy = case_when(Condition_spec == 'NoMatch'~ 1,
                                          Condition_spec == 'NoMatch'~ 1,
                                          T~0),
         Match_dummy = case_when(Condition_spec == 'Group_SumMatch'~ 1,
                                          Condition_spec == 'Random_SumMatch'~ 1,
                                          T~0),
         Group_SumMatch_dummy = if_else(Condition_spec == 'Group_SumMatch', 1, 0),
         Random_SumMatch_dummy = if_else(Condition_spec == 'Random_SumMatch',1,0),
         Group_PerfectMatch_dummy = if_else(Condition_spec == 'Group_PerfectMatch', 1, 0),
         Condition_spec = relevel(as.factor(Condition_spec),ref=4),
         Match = relevel(as.factor(Match),ref=2),
         Symb_First_RT = log(Symb_First_RT))%>% 
  mutate(Condition_spec = case_when(Condition_spec == 'Random_NoMatch'~ 'NoMatch',
                                    Condition_spec == 'Group_NoMatch'~ 'NoMatch',
                                    Condition_spec == 'Group_SumMatch' ~ 'Match',
                                    Condition_spec == 'Random_SumMatch' ~ 'Match',
                                    T~Condition_spec),
         grade_num = if_else(Grade=='K',0,as.numeric(Grade))) 

mod1 = lmer(Symb_First_RT ~Match  +(1+Match|Participant),
            data = ind_data_session_1,REML=F,
            control = lmerControl(
                           optimizer ='Nelder_Mead'))

ind_data_session_2 = kids_df %>% 
  group_by(Participant) %>% 
  mutate(trial_num = row_number()) %>% 
  ungroup() %>% 
  filter(Session=='002') %>% 
  filter(Symb_Correct==1) %>% 
  select(Participant, Match, Condition_spec, Symb_First_RT,Grade, age) %>% 
  mutate(NoMatch_dummy = case_when(Condition_spec == 'NoMatch'~ 1,
                                          Condition_spec == 'NoMatch'~ 1,
                                          T~0),
         Match_dummy = case_when(Condition_spec == 'Group_SumMatch'~ 1,
                                          Condition_spec == 'Random_SumMatch'~ 1,
                                          T~0),
         Group_SumMatch_dummy = if_else(Condition_spec == 'Group_SumMatch', 1, 0),
         Random_SumMatch_dummy = if_else(Condition_spec == 'Random_SumMatch',1,0),
         Group_PerfectMatch_dummy = if_else(Condition_spec == 'Group_PerfectMatch', 1, 0),
         Condition_spec = relevel(as.factor(Condition_spec),ref=4),
         Match = relevel(as.factor(Match),ref=2),
         Symb_First_RT = log(Symb_First_RT))%>% 
  mutate(Condition_spec = case_when(Condition_spec == 'Random_NoMatch'~ 'NoMatch',
                                    Condition_spec == 'Group_NoMatch'~ 'NoMatch',
                                    Condition_spec == 'Group_SumMatch' ~ 'Match',
                                    Condition_spec == 'Random_SumMatch' ~ 'Match',
                                    T~Condition_spec),
         grade_num = if_else(Grade=='K',0,as.numeric(Grade))) 

mod2 = lmer(Symb_First_RT ~Match  +(1+Match|Participant),
            data = ind_data_session_2,REML=F,
            control = lmerControl(
                           optimizer ='Nelder_Mead'))


test= ranef(mod1)$Participant %>% 
                    as.data.frame() %>% 
                    rownames_to_column("Participant") %>% 
                    mutate(
                           priming_effectMatch1 =(MatchMatch)) %>%
  select(Participant, priming_effectMatch1) %>% 
  inner_join(ranef(mod2)$Participant %>% 
                    as.data.frame() %>% 
                    rownames_to_column("Participant") %>% 
                    mutate(
                           priming_effectMatch2 =(MatchMatch)) %>%
  select(Participant, priming_effectMatch2),by='Participant') 

  cor.test(test$priming_effectMatch1, test$priming_effectMatch2)

```


### Figure 3B 

```{r}

prime_plot = kids_df_smarte %>% 
  select(priming_effectMatch,Grade,SMARTE_rcs_Fluency) %>% 
  unique() %>% 
  mutate(`Single-Digit Fluency Declile` = as.factor(ntile(SMARTE_rcs_Fluency,10)))%>% 
  ggplot(aes(x=priming_effectMatch, 
             y = `Single-Digit Fluency Declile`, 
             fill = `Single-Digit Fluency Declile`)) +
  geom_density_ridges()+
  theme_bw()+
  xlab('Numerical Congruence Effect')+
  scale_color_observable() +
  scale_fill_observable() +
  theme_bw()+
  theme(legend.position="none",
          axis.text=element_text(size=12),
        axis.title=element_text(size=14))


prime_plot

```

### Figure 3

```{r}

(Age_effect_PLOT_Bar|prime_plot )+
  plot_annotation(tag_levels='A')  & 
  theme(plot.tag = element_text(size = 25))

```



## Does SMARTE relate to priming?

```{r}

# Fit regression models to understand what variables predict priming effects

scale_this <- function(x) as.vector(scale(x))

priors = c(prior(normal(0, 10), class = "b"))

reg_data = kids_df_smarte %>% 
  mutate(priming_effect = priming_effectMatch,
         SMARTE_rcs_Fluency = scale(SMARTE_rcs_Fluency),
         SMARTE_rcs_Recall = scale(SMARTE_rcs_Recall),
         rcs_Subitizing = scale(rcs_Subitizing),
         grade_c = case_when(Grade=='K'~0,
                             T ~ as.numeric(Grade)))%>%
            mutate(priming_effect=scale(priming_effect))%>% 
             select(priming_effect, grade_c, age, SMARTE_rcs_Fluency,SMARTE_rcs_Recall,
                    rcs_Subitizing,rcs_Groupitizing,Participant) %>% 
             unique() %>% drop_na()


fit_no_group <- brm(priming_effect ~  SMARTE_rcs_Fluency+SMARTE_rcs_Recall + rcs_Subitizing + age , 
           data = reg_data ,
          family = gaussian(), prior = priors, sample_prior=T)


fit_no_sub <- brm(priming_effect ~  SMARTE_rcs_Fluency+SMARTE_rcs_Recall+ rcs_Groupitizing+ age , 
           data = reg_data ,
          family = gaussian(), prior = priors, sample_prior=T)


fit_no_flu <- brm(priming_effect ~ rcs_Subitizing+ SMARTE_rcs_Recall+ rcs_Groupitizing + age , 
           data = reg_data,
          family = gaussian(), prior = priors, sample_prior=T)

fit_no_recall <- brm(priming_effect ~ rcs_Subitizing+ rcs_Groupitizing + age , 
           data = reg_data,
          family = gaussian(), prior = priors, sample_prior=T)

# 
fit_no_grade = brm(priming_effect ~ SMARTE_rcs_Fluency+SMARTE_rcs_Recall+ rcs_Subitizing+rcs_Groupitizing + age ,
           data = reg_data,
          family = gaussian(), prior = priors, sample_prior=T)

# fit_no_age = brm(priming_effect ~ SMARTE_rcs_Fluency+SMARTE_rcs_Recall+ rcs_Subitizing+rcs_Groupitizing  + grade_c, 
#            data = reg_data ,
#           family = gaussian(), prior = priors, sample_prior=T)
```


```{r}


fit_0 = brm(priming_effect ~ 1, 
           data = reg_data ,
          family = gaussian(),  sample_prior=T)

fit_1 = brm(priming_effect ~ rcs_Groupitizing, 
           data = reg_data ,
          family = gaussian(), prior = priors, sample_prior=T)

fit_2 = brm(priming_effect ~ rcs_Groupitizing  + rcs_Subitizing, 
           data = reg_data ,
          family = gaussian(), prior = priors, sample_prior=T)

fit_3 = brm(priming_effect ~ SMARTE_rcs_Fluency+ rcs_Subitizing+rcs_Groupitizing  , 
           data = reg_data,
          family = gaussian(), prior = priors, sample_prior=T)

fit_4 = brm(priming_effect ~ SMARTE_rcs_Recall + SMARTE_rcs_Fluency+ rcs_Subitizing+rcs_Groupitizing  , 
           data = reg_data,
          family = gaussian(), prior = priors, sample_prior=T)

fit_5 = brm(priming_effect ~ age + SMARTE_rcs_Fluency+ rcs_Subitizing+rcs_Groupitizing  , 
           data = reg_data,
          family = gaussian(), prior = priors, sample_prior=T)



```


```{r}




test_wald(fit_0, fit_1)
test_wald(fit_1, fit_2)
test_wald(fit_3, fit_2)
test_wald(fit_3, fit_4)
test_wald(fit_3, fit_5)



```


### Figure 4A

```{r}
# Fit the reduced model using brms


reg_plot_kids = (summary(fit_5))$fixed %>% 
  rownames_to_column('Predictor') %>% 
  mutate(Predictor = case_when(Predictor == 'rcs_Subitizing' ~ 'Subitizing',
                              Predictor == 'rcs_Groupitizing'~ 'Groupitizing',
                              Predictor == 'SMARTE_rcs_Fluency'~ 'Single-Digit Fluency',
                              Predictor == 'SMARTE_rcs_Recall'~ 'Mixed-Digit Arithmetic',
                              Predictor == 'age' ~ 'Age',
                              Predictor == 'grade_c' ~ 'Grade',
                              T ~ Predictor)) %>% 
  filter(Predictor != 'Intercept') %>% 
  # arrange(Estimate) %>%    # First sort by val. This sort the dataframe but NOT the factor levels
  mutate(Predictor=factor(Predictor, levels=Predictor), # This trick update the factor levels
         # sig = `Pr(>|t|)` < 0.05
         ) %>%   
  ggplot(aes(x=Estimate, y = Predictor))+
  geom_point()+
  ylab("")+
  geom_linerange(aes(xmin=`l-95% CI`, xmax=`u-95% CI`))+
  geom_vline(xintercept = 0, linetype = 3, alpha=0.5)+
  xlab("Regression Coefficient")+
  theme_classic()+
  guides(alpha='none')+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))


```


### Does Priming Effect Mediate the relationship between groupitizing and fluency?



```{r}

test_med = kids_df_smarte %>% 
  filter(Symb_Correct==T) %>% 
  group_by(Participant) %>% 
  mutate(mean_symb_rt = mean(Symb_First_RT, na.rm=T))%>% 
  mutate(priming_effect = priming_effectMatch) %>% 
  select(priming_effect, Grade, age, Participant, SMARTE_rcs_Fluency,
         SMARTEScore_Recall,rcs_Groupitizing, rcs_Subitizing,rcs_Random,
         mean_symb_rt)%>% 
  unique() %>% 
  ungroup() %>%
  dplyr::mutate(across(c('rcs_Subitizing', 'rcs_Groupitizing', 'SMARTE_rcs_Fluency', 'SMARTEScore_Recall','priming_effect','rcs_Random'),  scale))

# Fit Bayesian mediation model in brms
f1 <- bf(priming_effect ~   rcs_Groupitizing  + rcs_Subitizing + age)
f2 <- bf(SMARTE_rcs_Fluency ~ priming_effect + rcs_Groupitizing + rcs_Subitizing + age)
m2 <- brm(f1 + f2 + set_rescor(FALSE),
          data = test_med, refresh = 0, sample_prior=T,seed = 42)

mediation(m2, sims=1000, ci=.95)


# Fit Bayesian mediation model in brms -- random enumeration as mediator?
f1 <- bf(rcs_Random ~   rcs_Groupitizing + rcs_Subitizing +  age)
f2 <- bf(SMARTE_rcs_Fluency ~ rcs_Random + rcs_Groupitizing + rcs_Subitizing + age)
m3 <- brm(f1 + f2 + set_rescor(FALSE), data = test_med, refresh = 0, sample_prior=T,
          seed = 42)

mediation(m3, sims=1000, ci=.95)
```


### Figure 4B

```{r}

med_plot_kids =  ggplot() +
  geom_segment(aes(x = 1.5, y = 0.9, xend = 2.1, yend = 1.3), 
               arrow = arrow(length = unit(0.3, "cm"))) + # X to M
  geom_segment(aes(x = 2.1, y = 1.3, xend = 2.7, yend = 0.9), 
               arrow = arrow(length = unit(0.3, "cm"))) + # M to Y
  geom_segment(aes(x = 1.8, y =  0.85, xend = 2.4, yend = 0.85),
               arrow = arrow(length = unit(0.3, "cm"))) + # X to Y
  geom_rect(aes(xmin = 1.2, xmax = 1.8, ymin = 0.8, ymax = 0.9), 
            fill = 'white', color='black') + # Rectangle for X
  geom_rect(aes(xmin = 1.8, xmax = 2.4, ymin = 1.3, ymax = 1.4), 
            fill = 'white', color='black') + # Rectangle for M
  geom_rect(aes(xmin = 2.4, xmax = 3, ymin = 0.8, ymax = 0.9), 
            fill = 'white', color='black') + # Rectangle for Y
  geom_text(aes(x = 1.5, y = 0.85, label = "Groupitizing Ability")) +
  geom_text(aes(x = 2.1, y = 1.35, label = "Priming Effect")) +
  geom_text(aes(x = 2.7, y = 0.85, label = "Single-Digit Fluency")) + # c = c' + ab
  geom_text(aes(x = 1.8, y = 1.1, label = "0.374"),hjust = 1.3) + # a
  geom_text(aes(x = 2.4, y = 1.1, label = "0.671"),hjust = -0.3) + # mediator effect (b)
  geom_text(aes(x = 2.1, y = 0.89, label = "c = 0.626")) + # total effect (c)
  geom_text(aes(x = 2.1, y = 0.81, label = "c' = 0.375")) + # direct effect (c')
  theme_void()

## Make regression + mediation plot
(reg_plot_kids | med_plot_kids) +
  plot_annotation(tag_levels='A')  & 
  theme(plot.tag = element_text(size = 25))


```



# Supplemental Figures
## Supplemental Figure 1

```{r}

no_outliers_data_smarte %>% 
  ggplot(aes(x=rcs_Groupitizing, y = Grade, fill = Grade)) +
  geom_density_ridges()+
  theme_bw()+
  xlab('Individual Groupitizing Skill (Correct Responses per Minute)')+
  scale_color_d3() +
  scale_fill_d3() +
  theme_bw()+
  theme(legend.position = "top")

```