---
title: "Transfer -- Adult Sample"
output: html_document
date: "2025-06-03"
---

```{r warning = FALSE, include = FALSE, max.height = '100px'}
#Load libraries.

library(ggpubr)
require(readxl)
require(DT)
require(dplyr)
require(ggplot2)
require(ggsci)
require(lme4)
require(lmerTest)
require(multcomp)
require(emmeans)
library(tidyverse)
library(BayesFactor)
library(bayestestR)
library(broom)
library(patchwork)
library(ggridges)
library(psych)
library(brms)
library(reshape2)
select <- dplyr::select


```


# Load Data

```{r}
no_outliers_data_smarte = read_csv("clean_trial_data_smarte_full.csv") %>% 
    mutate(Grade = factor(Grade, levels=c("K","1","2","3","4","5","7","A"))) 

no_outliers_data = read_csv("clean_trial_data_full.csv") %>% 
    mutate(Grade = factor(Grade, levels=c("K","1","2","3","4","5","7","A"))) 


adult_df = no_outliers_data %>% 
  filter(Group=='Adults') %>% 
  mutate(Congruence = if_else(Match=='Match',
                              'Numerical Congruence', 'Numerical Incongruence')) %>% 
  inner_join(demos, by='Participant')

```

# Descriptive Statistics

```{r}

# Accuracy Stats
adult_df %>% 
  group_by(Participant) %>% 
  summarise(acc_dots = sum(Array_Correct)/n(),
            acc_sym = sum(Symb_Correct)/n()) %>% 
  ungroup() %>% 
  summarise(mean_acc_dot = mean(acc_dots, na.rm=T),
            sd_acc_dot = sd(acc_dots, na.rm=T),
            mean_acc_sym = mean(acc_sym, na.rm=T),
            sd_acc_sym = sd(acc_sym, na.rm=T))


# Accuracy Stats
adult_df %>% 
  filter(Symb_Correct==T) %>% 
  filter(Array_Correct==T) %>% 
  summarise(mean_rt_dot = mean(Array_First_RT, na.rm=T),
            sd_rt_dot = sd(Array_First_RT, na.rm=T),
            mean_rt_sym = mean(Symb_First_RT, na.rm=T),
            sd_rt_sym = sd(Symb_First_RT, na.rm=T))

stats_df = adult_df %>% 
  filter(Symb_Correct==T) %>% 
  filter(Array_Correct==T) %>% 
  mutate(Array_First_RT = as.numeric(Array_First_RT),
         Symb_First_RT = as.numeric(Symb_First_RT))

t.test(stats_df$Array_First_RT, stats_df$Symb_First_RT)
ttestBF(stats_df$Array_First_RT, stats_df$Symb_First_RT)



```


## Do adults show sensitivity to structural congruence in cardinal priming effects?

Are there impacts of grouping strucure on cardinal priming, relative to baseline (random no match)

### Figure 5A

```{r warning = FALSE, echo = FALSE}



DATASET <- do.call(data.frame, aggregate(Symb_First_RT ~  Condition_spec ,
                                         data = adult_df %>% 
                                           filter(Symb_Correct==1),  
                                           # filter(Condition!='NoMatch') %>% 
                                           # filter(Match=='Match') ,
                                           FUN = function(x) c(Mean = mean(x), 
                                                               L95 = mean(x) - 1.96 * sd(x) / sqrt(length(x)),
                                                               U95 = mean(x) + 1.96 * sd(x) / sqrt(length(x)))))


FIG2A_PLOT_Bar = DATASET %>% 
  filter(Symb_First_RT.Mean < 2) %>% 
  mutate(Condition = case_when(Condition_spec=='NoMatch'~ 'Not Matching',
                               Condition_spec=='Random_SumMatch'~ 'Ungrouped Whole Set Matching',
                               Condition_spec=='Group_SumMatch'~ 'Grouped Whole Set Matching',
                               Condition_spec=='Group_PerfectMatch'~ 'Grouped Subgroup Matching')) %>% 
  mutate(Condition = factor(Condition,levels=c('Not Matching',
                                               'Ungrouped Whole Set Matching',
                                               'Grouped Whole Set Matching',
                                               'Grouped Subgroup Matching')))%>% 
ggplot( aes(y = Symb_First_RT.Mean,
            x = Condition,color = Condition, fill = Condition)) +
geom_col(position='dodge', aes(color = Condition, fill = Condition),alpha=0.8)+
geom_errorbar(aes(x=Condition, ymin = Symb_First_RT.L95, ymax = Symb_First_RT.U95),
              position=position_dodge(.9), width=0.2,color='black')+
scale_color_npg() +
scale_fill_npg() +
labs(x = 'Condition', y = '(Correct) Response times (ms)') +
theme_classic()+
  theme(legend.key.size = unit(1, 'cm'), #change legend key size
        legend.title = element_text(size=14), #change legend title font size
        legend.text = element_text(size=14),
        legend.position='bottom',
        axis.text=element_text(size=15),
        axis.text.x = element_blank(),
        axis.title=element_text(size=17))+
  guides(fill = guide_legend(nrow = 2),
         color = guide_legend(nrow = 2))

FIG2A_PLOT_Bar

```
#### Statistical Tests

```{r warning = FALSE, echo = FALSE, }

set.seed(202111208)

stats_df_match = adult_df %>% 
  filter(Symb_Correct==1) %>% 
  mutate(Condition_spec = as.factor(Condition_spec),
         Participant = as.factor(Participant))


# Fit the full model without interaction.
summary(aov(Symb_First_RT ~ Condition_spec, data = stats_df_match))
BF = anovaBF(Symb_First_RT ~  Condition_spec , data = stats_df_match, whichModels = "top")

1/BF


emmeans(lm(Symb_First_RT ~ Condition_spec, data = stats_df_match), 
        list(pairwise ~ Condition_spec),
        adjust = "fdr",
        pbkrtest.limit = 3486)

conditions = unique((stats_df_match %>%
                      mutate(Condition_spec = as.character(Condition_spec)))$Condition_spec)

for(i in 1:length(conditions)){
  for(j in i:length(conditions)){
    Sys.sleep(0.1)
    
    if(i!=j){
        print(paste(conditions[i], conditions[j]))
        print(ttestBF(x=subset(stats_df_match, Condition_spec == conditions[i])$Symb_First_RT,
                      y=subset(stats_df_match, Condition_spec == conditions[j])$Symb_First_RT))
    }
  }
}

stats_df_match %>% 
  group_by(Condition_spec) %>% 
  summarise(mean_rt = mean(Symb_First_RT, na.rm=T),
            sd_rt = sd(Symb_First_RT, na.rm=T))

```

## Is cardinal priming related to groupitizing skill

Compare difference between match/no-match and relate to groupitizing


```{r}

# set up data for individual priming effects model
ind_data = adult_df %>%
  filter(Symb_Correct==1) %>%
  select(Participant, Match, Condition_spec, Symb_First_RT) %>%
  mutate(NoMatch_dummy = if_else(Match == 'NoMatch', 1, 0),
         Match_dummy = if_else(Match == 'Match', 1, 0),
         Match = relevel(as.factor(Match), ref=1),,
         Symb_First_RT = log(Symb_First_RT))

mod0 = lmer(Symb_First_RT ~ Match + (1|Participant), data = ind_data)


mod1 = lmer(Symb_First_RT ~ Match + (Match|Participant), data = ind_data)
summary(mod1)


adult_df_smarte = adult_df %>% 
  inner_join(ranef(mod1)$Participant %>% 
                    as.data.frame() %>% 
                    rownames_to_column("Participant") %>% 
                    mutate(priming_effect = 0.10466-`MatchNo Match`,
                           enumeration_effect = 0.28663+`(Intercept)`),
             by = 'Participant') %>% 
  inner_join(symbolic_smarte_scores, by='Participant') %>% 
  inner_join(subitizing_df, by='Participant') %>% 
  inner_join(symbolic_module_scores, by='Participant') %>% 
  inner_join(group_rcs_df, by='Participant') %>% 
  inner_join(diff_df, by='Participant')

summary(mod1)

```



```{r}

scale_this <- function(x) as.vector(scale(x))

priors = c(prior(normal(0, 10), class = "b"))

reg_data = adult_df_smarte %>% 
  mutate(priming_effect = scale(priming_effect),
         SMARTE_rcs_Fluency = scale(SMARTE_rcs_Fluency),
         SMARTE_rcs_Recall = scale(SMARTE_rcs_Recall),
         rcs_Subitizing = scale(rcs_Subitizing))%>%
            mutate(priming_effect=scale(priming_effect))%>% 
             select(priming_effect, SMARTE_rcs_Fluency,SMARTE_rcs_Recall,
                    rcs_Subitizing,rcs_Groupitizing) 

fit_no_group <- brm(priming_effect ~  SMARTE_rcs_Fluency+ SMARTE_rcs_Recall+ rcs_Subitizing, 
           data = reg_data, 
          family = gaussian(), prior = priors, sample_prior=T)


fit_no_sub <- brm(priming_effect ~  SMARTE_rcs_Fluency+ SMARTE_rcs_Recall+ rcs_Groupitizing, 
           data = reg_data,
          family = gaussian(), prior = priors, sample_prior=T)


fit_no_flu <- brm(priming_effect ~ rcs_Subitizing+ SMARTE_rcs_Recall+ rcs_Groupitizing, 
           data = reg_data,
          family = gaussian(), prior = priors, sample_prior=T)

fit_no_recall = brm(priming_effect ~ SMARTE_rcs_Fluency+ rcs_Subitizing+rcs_Groupitizing, 
           data = reg_data,
          family = gaussian(), prior = priors, sample_prior=T)


fit_adult = brm(priming_effect ~  rcs_Subitizing+rcs_Groupitizing+SMARTE_rcs_Fluency+SMARTE_rcs_Recall, 
           data = reg_data, seed = 42, 
          family = gaussian(), prior = priors, sample_prior=T)

bayes_factor(fit_adult, fit_no_flu)
bayes_factor(fit_adult, fit_no_group)
bayes_factor(fit_adult, fit_no_sub)
bayes_factor(fit_adult, fit_no_recall)

print(summary(fit_adult), digits=5)

fit_5 = brm(priming_effect ~ SMARTE_rcs_Fluency+ rcs_Subitizing+rcs_Groupitizing  , 
           data = reg_data,
          family = gaussian(), prior = priors, sample_prior=T)

```
### Figure 5B

```{r}


model_plot = as.data.frame(summary(fit_5)$fixed)%>% 
  rownames_to_column('Predictor') %>% 
  mutate(Predictor = case_when(Predictor == 'Grade5'~ 'Grade 5',
                              Predictor == 'Grade7'~ 'Grade 7',
                              Predictor == 'GradeA'~ 'Adult',
                              Predictor == 'rcs_Subitizing' ~ 'Subitizing',
                              Predictor == 'SMARTE_rcs_Recall' ~ 'Mixed-Digit Arithmetic',
                              Predictor == 'rcs_Groupitizing'~ 'Groupitizing',
                              Predictor == 'SMARTE_rcs_Fluency'~ 'Single-Digit Fluency',
                              Predictor == 'SMARTEScore_Recall'~ 'Mixed-Digit Arithmetic',
                              T ~ Predictor)) %>% 
  filter(Predictor != 'Intercept') %>%
  # arrange(Estimate) %>%    # First sort by val. This sort the dataframe but NOT the factor levels
  mutate(Predictor=factor(Predictor, levels=Predictor), # This trick update the factor levels
         # sig = `Pr(>|t|)` < 0.05
         ) %>%   
  ggplot(aes(x=Estimate, y = Predictor))+
  geom_point()+
  geom_linerange(aes(xmin=`l-95% CI`, xmax=`u-95% CI`))+
  geom_vline(xintercept = 0, linetype = 3, alpha=0.5)+
  xlab("Regression Coefficient")+
  theme_classic()+
  guides(alpha='none')+
  theme(axis.text.y = element_text(size=11))

model_plot

```


## Does priming effect mediate the relationship between groupitizing and single-digit fluency?

```{r}
## Standardize these predictors. 
mod_data = adult_df_smarte %>% 
  select(priming_effect, Grade, Participant, SMARTE_rcs_Fluency,rcs_Random,
         Subitizing,SMARTEScore_Recall,rcs_Groupitizing, rcs_Subitizing)%>% 
  ungroup() %>%
  dplyr::mutate(across(c('rcs_Subitizing', 'rcs_Groupitizing', 'SMARTE_rcs_Fluency', 'SMARTEScore_Recall','priming_effect','rcs_Random'),  scale))


# Fit Bayesian mediation model in brms
f1 <- bf(priming_effect ~   rcs_Groupitizing +rcs_Subitizing )
f2 <- bf(SMARTE_rcs_Fluency ~ priming_effect + rcs_Groupitizing +rcs_Subitizing)
m2 <- brm(f1 + f2 + set_rescor(FALSE), data = mod_data, refresh = 0, sample_prior=T,
          seed = 42)

mediation(m2, sims=1000, ci=.95)


# Fit Bayesian mediation model in brms
f1 <- bf(rcs_Random ~   rcs_Groupitizing +rcs_Subitizing)
f2 <- bf(SMARTE_rcs_Fluency ~ rcs_Random + rcs_Groupitizing +rcs_Subitizing)
m3 <- brm(f1 + f2 + set_rescor(FALSE), data = mod_data %>% unique(), refresh = 0, sample_prior=T,
          seed = 42)

mediation(m3, sims=1000, ci=.95)

m3


```

### Figure 5C

```{r}

med_plot =  ggplot() +
  geom_segment(aes(x = 1.5, y = 0.9, xend = 2.1, yend = 1.3), 
               arrow = arrow(length = unit(0.3, "cm"))) + # X to M
  geom_segment(aes(x = 2.1, y = 1.3, xend = 2.7, yend = 0.9), 
               arrow = arrow(length = unit(0.3, "cm"))) + # M to Y
  geom_segment(aes(x = 1.8, y =  0.85, xend = 2.4, yend = 0.85),
               arrow = arrow(length = unit(0.3, "cm"))) + # X to Y
  geom_rect(aes(xmin = 1.2, xmax = 1.8, ymin = 0.8, ymax = 0.9), 
            fill = 'white', color='black') + # Rectangle for X
  geom_rect(aes(xmin = 1.8, xmax = 2.4, ymin = 1.3, ymax = 1.4), 
            fill = 'white', color='black') + # Rectangle for M
  geom_rect(aes(xmin = 2.4, xmax = 3, ymin = 0.8, ymax = 0.9), 
            fill = 'white', color='black') + # Rectangle for Y
  geom_text(aes(x = 1.5, y = 0.85, label = "Groupitizing Ability")) +
  geom_text(aes(x = 2.1, y = 1.35, label = "Priming Effect")) +
  geom_text(aes(x = 2.7, y = 0.85, label = "Single-Digit Fluency")) + # c = c' + ab
  geom_text(aes(x = 1.8, y = 1.1, label = "0.406"),hjust = 1.3) + # a
  geom_text(aes(x = 2.4, y = 1.1, label = "0.502"),hjust = -0.3) + # mediator effect (b)
  geom_text(aes(x = 2.1, y = 0.89, label = "c = 0.406")) + # total effect (c)
  geom_text(aes(x = 2.1, y = 0.81, label = "c' = 0.202")) + # direct effect (c')
  theme_void()

med_plot

```

## Figure 5 Full

```{r}

(FIG2A_PLOT_Bar | model_plot/med_plot) +
  plot_annotation(tag_levels='A')  & 
  theme(plot.tag = element_text(size = 25))

```


## Supplemental Figure 2

```{r}

adult_df_smarte_cor_plot = adult_df_smarte %>% 
  select(-Subitizing) %>% 
  rename( `Priming Effect` = priming_effect,
          `Single-Digit Fluency` = SMARTE_rcs_Fluency,
          `Multi-Digit Fluency` = SMARTE_rcs_Recall,
          Groupitizing = rcs_Groupitizing,
          Subitizing = rcs_Subitizing)


corr_cols = c('Priming Effect', 'Single-Digit Fluency',
         'Multi-Digit Fluency', 'Groupitizing','Subitizing')

# Initialize an empty matrix
n <- length(corr_cols)
result_matrix <- matrix(NA, n, n)
rownames(result_matrix) <- corr_cols
colnames(result_matrix) <- corr_cols

for(i in 1:length(corr_cols)){
  for(j in i:length(corr_cols)){
  
    if(i!=j){
      
      cor_value = round(cor(adult_df_smarte_cor_plot[[corr_cols[i]]],
                            adult_df_smarte_cor_plot[[corr_cols[j]]]),3)
      bf_value = extractBF(correlationBF(adult_df_smarte_cor_plot[[corr_cols[i]]],
                                         adult_df_smarte_cor_plot[[corr_cols[j]]],
                                         rscale='medium'))$bf
      if(bf_value>100){
        bf_value='BF >100'
      }
      # Populate lower triangle with correlation values
      result_matrix[j, i] <- as.numeric(cor_value)  # Note: (j, i) for lower triangle
      
      # Populate upper triangle with Bayes Factors
      result_matrix[i, j] <- bf_value  # Note: (i, j) for upper triangle
    }
    else{
      result_matrix[i,j] <- 0
    }
  }
}

# Reshape the matrix into a long format
df_long <- melt(result_matrix, na.rm = TRUE)
colnames(df_long) <- c("Var1", "Var2", "Value")

# Add a column to differentiate Correlation and Bayes Factor
df_long$Type <- ifelse(upper.tri(result_matrix, diag = FALSE)[cbind(match(df_long$Var1,
                                                                          rownames(result_matrix)), 
                                                                    match(df_long$Var2,
                                                                          colnames(result_matrix)))],
                       "BF", "Correlation")

df_long = df_long %>% 
  mutate(cor_val = if_else(Type=='Correlation',as.numeric(Value),NA))

# %>% 
#   arrange(Var1,Var2,Type)

# Plot the heatmap
cor_plot = ggplot(data = df_long, aes(x = Var2, y = Var1, fill = cor_val)) +
  geom_tile(alpha=0.75) +
  geom_text(aes(label = case_when(Type == "BF"~ Value, 
                                  cor_val==0 ~ " ",
                                  T~ Value)), 
            size = 4.5, color = "black") +
  scale_fill_gradient2(low = "blue", mid = 'white',high = "red",
                       midpoint = 0, na.value = 'lightgrey',name = "Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text = element_text(size=12)) +
  labs(x = NULL, y = NULL) +
  coord_fixed()


cor_plot


```
